Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-06-30 sattose/paper.tex
Better explain T2R

\begin{equation}\label{eq:typerelation}
\text{Cloned statements: } T1R \subseteq T2R \subseteq T3R
\end{equation}

@@

\subsubsection{Type 2R clones}\label{sec:type2r}
We tackle the previously outlined shortcomings of type 2 clones to be able to detect such clones that can and should be refactored. All rules that apply to type 1R clones also apply to type 2R clones. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold. Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types. As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.

We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored. Our definition ensures functional similarity by applying the following changes to type 2 clones:

@@

>>>>

\begin{equation}\label{eq:typerelation}
T1R \subseteq T2R \subseteq T3R
\end{equation}

@@

\subsubsection{Type 2R clones}\label{sec:type2r}
We tackle the previously outlined shortcomings of type 2 clones to be able to detect such clones that can and should be refactored. All rules that apply to type 1R clones also apply to type 2R clones. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold as a tradeoff exists in the refactoring of such differences. Furthermore, type 2R clones allow any variability in method names and class/enum/interface names. This is because, if the body of a method/class/enum/interface equals the body of another, but only their names differ, this can be refactored without a design tradeoff.

@@

\begin{equation}\label{eq:typerelation2}
T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
\end{equation}
